Summary Tables ITHIMR

### 2019-04-29 summary_tables_PA_AP.Rmd
changes made to summary code

```{r, message=FALSE, warning=FALSE}
#library(INLA)     #loading the INLA package
library(ggplot2)  #loading ggplot package for plotting graphs
library(knitr)     
library(tidyr)
library(dplyr)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
io <- readRDS("V:/Group/RG_PHM/ITHIM-R/results/multi_city/io.rds")

@@

>>>>

```{r, message=FALSE, warning=FALSE}
#library(INLA)     #loading the INLA package
library(ggplot2)  #loading ggplot package for plotting graphs
library(knitr)     
library(tidyr)
library(dplyr)
library(kableExtra)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
io <- readRDS("results/multi_city/io.rds")

@@

  summary %>%
  kable() %>%
  kable_styling()
